Enforced Invariant Confluence

### 2018-03-12 doc/paper_redux/sufficient_conditions.tex
Wrote up student example in more detail.

\begin{example}
  \todo{Write this up in full.}
  Imagine we are building a system to group students together. We have a relation
  of (student id, grade) and a map (group id -> set of student ids). We want to
  enforce the invariant that every student in every group is in the same grade
  and that all groups are non-empty. If we start off with an initially empty
  mapping, then there are conflicts. If we start off with at least one student
  mapped into each group, then there are not any conflicts.
\end{example}

>>>>

\begin{example}
  Imagine that we have a set $P$ of students ($P$ is for pupils) and that we
  are trying to assign students into groups. We have a state based object $O =
  (S, \join)$ where each state $s \in S$ in a dictionary mapping a group id $1,
  \ldots, n$ to some subset of $P$. For example, if $P = \set{a, b, c}$, then
  $s$ might be $\set{1 \mapsto \set{a, b}, 2 \mapsto \set{c}}$. We join two
  dictionaries by taking a group-wise union. That is, $(s_1 \join s_2)(i) =
  s_1(i) \cup s_2(i)$.

  Furthermore assume each student $p$ has a year $year(p)$ (e.g. 5th grade, 4th
  grade). Our invariant $I$ is that every group of students is in the same
  year. That is, for every state $s$ and every $1 \leq i \leq n$, every student
  in $s(i)$ belongs to the same year.
  %
  Our set $T$ of transactions includes transactions which allow us to add any
  number of students to any number of groups.
  %
  Let $P = \set{a, b, \ldots, z}$ and $n = 3$. Our start state is $s_0 = \set{1
  \mapsto \set{a}, 2 \mapsto \set{b}, 3 \mapsto \set{c}}$.

  Some thought shows that O is \sTIconfluent{}. However, $O$ is not \Iclosed{}. Let
  \[
    s_1 = \set{1 \mapsto \set{x}, 2 \mapsto \emptyset, 3 \mapsto \emptyset}
    \qquad
    s_2 = \set{1 \mapsto \set{y}, 2 \mapsto \emptyset, 3 \mapsto \emptyset}
  \]
  where $year(x) \neq year(y)$. $I(s_1)$ and $I(s_2)$, but $\lnot I(s_1 \join
  s_2)$.
\end{example}
